---
title: "Student Success Dashboard Group 2"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
#runtime: shiny
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT #for better tables
               )

#read in data
```

# Student Success Project Overview {data-orientation=columns}

Description of project

# Salary Trends {data-orientation=columns}

## Column {data-width=600}

### Average FSB Graduate Salary Over Time 

```{r,echo=FALSE}

```

### Average FSB Graduate Salary Over Time by Primary Major 

```{r,echo=FALSE}

```

## Column {data-width=300}

### Overall Change in Placement Rate

```{r,echo=FALSE}

```

# Placement Trends {data-orientation=columns}

## Column {data-width=600}

### Average FSB Graduate Placement Rate Over Time

```{r,echo=FALSE}

```

### Average FSB Graduate Salary Over Time by Primary Major 

```{r}

```

## Column {data-width=300}

### Overall Change in Placement Rate

```{r,echo=FALSE}

```