---
title: "Student Success Dashboard Group 2"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
#runtime: shiny
---

```{=html}
<style>                    

.navbar, [data-toggle=tab], .navbar-brand {

  background-color: red!important;

  border-color: black;

  color: white!important;

}

 

.navbar .navbar-nav > li > a:hover, .navbar .navbar-nav > li > a:focus {

  background-color: crimson!important;

}

 

.navbar .navbar-nav > li > a:active {

  background-color: crimson!important;

}

</style>
```
```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT #for better tables
               )

student_data = read_csv("CleanedStudentSuccessData.csv")
```

# Project Overview {data-orientation="columns"}

**Research Questions**

The main questions we are trying to answer from the data are: (1) What are the starting salary trends for FSB graduates as a whole and for individual majors? (2) What are the placement trends for FSB graduates overall and for each FSB major?

**FSB Starting Salary Trends**

-   2020 had the highest average starting salary despite the pandemic

When looking at the average salary of an FSB graduate throughout the years 2019-2021, one noticeable year was 2020. Of the three years, 2020 had the highest average starting salary (\$60,560) for FSB graduates. According to the NACE Salary Survey ([wpi.edu-2020](https://www.wpi.edu/sites/default/files/inline-image/Offices/Career-Development-Center/2020-nace-salary-survey-winter.pdf)), which shares starting salary projections for the 2020 new college graduates, they predicted an average salary of \$57,940 for Bachelor's Degree Graduates in Business. The starting salary for FSB graduates in 2020 was even above predictions by about \$2,600.

**Major Salary and Placement Trends**

-   Average salary from FSB graduates is consistent from 2019-2020

Looking further into the average starting salary for FSB Graduates by their major, all majors except Business Analytics saw a salary increase from 2019 to 2020. Most majors peaked in 2020 and then saw a decline in starting salaries for 2021, with the exception of Information Systems, Business Analytics, and Human Capital Management & Leadership. For 2019, those who majored in Business Analytics had the highest average starting salary of \$71,000 and

**References**

# Salary Trends {data-orientation="columns"}

## Column {data-width="600"}

### Average FSB Graduate Salary Over Time

```{r,echo=FALSE}
library(tidyverse)  
library(ggplot2)
library(dplyr)

avg_salary_data <- student_data %>%
  group_by(year.x) %>%
  summarise(avg_salary = mean(survey_salary, na.rm = TRUE))

# Bar plot
p <- ggplot(avg_salary_data, aes(x = year.x, y = avg_salary)) +
  geom_bar(stat = "identity", fill = "darkred") +
  labs(x = "Year",
       y = "Average Salary") +
  theme_bw()

ggplotly(p)
```

### Average FSB Graduate Salary Over Time by Primary Major

```{r,echo=FALSE}
avg_salary_data <- student_data %>%
  group_by(year.x, major1) %>%
  summarise(avg_salary = mean(survey_salary, na.rm = TRUE))

# Time Series
p=ggplot(avg_salary_data, aes(x = year.x, y = avg_salary, color = major1)) +
  geom_line() +
  labs(x = "Year",
       y = "Average Salary",
       color = "Major") +
  theme_bw()
ggplotly(p)
```

## Column {data-width="300"}

### Major with the Most Growth in Salary

```{r,echo=FALSE}
avg_salary_growth <- student_data %>%
  group_by(major1, year.x) %>%
  summarise(avg_salary = mean(survey_salary, na.rm=TRUE)) %>%
    group_by(major1) %>% 
    summarise(
    first_avg_salary = first(avg_salary),
    last_avg_salary = last(avg_salary),
    growth_rate = ((last_avg_salary - first_avg_salary) / first_avg_salary)
  ) %>%
  arrange(desc(growth_rate)) %>%
  slice(1) %>%
  ggplot(aes(x = "", y = growth_rate, fill = major1)) +
  geom_col(width = .7) +
  geom_text(aes(label = scales::percent(growth_rate)),
            position = position_stack(vjust = 0.5)) +
  labs(
    x = NULL,
    y = "Percentage Increase",
    fill = "Major"
  ) +
  theme_minimal() +
  theme(legend.position = "top", legend.box = "horizontal", legend.margin = margin(0, 0, 0, 0))

ggplotly(avg_salary_growth)
```

### Major with the Least Growth in Salary

```{r,echo=FALSE}
avg_salary_growth <- student_data %>%
  group_by(major1, year.x) %>%
  summarise(avg_salary = mean(survey_salary, na.rm=TRUE)) %>%
    group_by(major1) %>% 
    summarise(
    first_avg_salary = first(avg_salary),
    last_avg_salary = last(avg_salary),
    growth_rate = ((last_avg_salary - first_avg_salary) / first_avg_salary)
  ) %>%
  arrange(growth_rate) %>%
  slice(1) %>%
  ggplot(aes(x = "", y = growth_rate, fill = major1)) +
  geom_col(width = .7) +
  geom_text(aes(label = scales::percent(growth_rate)),
            position = position_stack(vjust = 0.5)) +
  labs(
    x = NULL,
    y = "Percentage Decrease",
    fill = "Major"
  ) +
  theme_minimal() +
  theme(legend.position = "top", legend.box = "horizontal", legend.margin = margin(0, 0, 0, 0))

ggplotly(avg_salary_growth)
```

# Placement Trends {data-orientation="columns"}

## Column {data-width="600"}

### Average FSB Graduate Placement Rate Over Time

```{r,echo=FALSE}
bar_chart_data <- student_data %>%
  filter(survey_plans != "unknown") %>% 
  group_by(year.x) %>%
  summarise(placement_rate = sum(placement) / n())

# Bar Chart
p = ggplot(bar_chart_data, aes(x = year.x, y = placement_rate)) +
  geom_bar(stat = "identity", fill = "darkred") +
  labs(x = "Year",
       y = "Placement Rate") +
  theme_bw()
ggplotly(p)
```

### Average FSB Graduate Placement Rate Over Time by Primary Major

```{r,echo=FALSE}
time_series_data <- student_data %>%
  filter(survey_plans != "unknown") %>% 
  group_by(year.x, major1) %>%
  summarise(placement_rate = sum(placement) / n())

# Time Series Chart
p=ggplot(time_series_data, aes(x = year.x, y = placement_rate, color = major1)) +
  geom_line() +
  labs(x = "Year",
       y = "Placement Rate",
       color = "Major") +
  theme_bw()
ggplotly(p)
```

## Column {data-width="300"}

### Major with the Most Growth in Placement Rate

```{r,echo=FALSE}
p = student_data %>%
  group_by(major1, year.x) %>%
  summarise(placement_rate = sum(placement) / n()) %>%
  group_by(major1) %>%
  summarise(max_increase = max(placement_rate) - min(placement_rate)) %>%
  arrange(desc(max_increase)) %>%
  slice(1) %>%
  ggplot(aes(x = "", y = max_increase, fill = major1)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = scales::percent(max_increase)),
            position = position_stack(vjust = 0.5)) +
  labs(
       x = NULL,
       y = "Percentage Increase",
       color="Major") +
  theme_minimal() +
  theme(legend.position = "top", legend.box = "horizontal", legend.margin = margin(0, 0, 0, 0))

p_plotly <- ggplotly(p)
p_plotly <- p_plotly %>%
  layout(legend = list(title = list(text = "Major")))
p_plotly
```

### Major with the Least Growth in Placement Rate

```{r,echo=FALSE}
p <- student_data %>%
  group_by(major1, year.x) %>%
  summarise(placement_rate = sum(placement) / n()) %>%
  group_by(major1) %>%
  summarise(
    initial_placement_rate = first(placement_rate),
    final_placement_rate = last(placement_rate),
    max_increase = final_placement_rate - initial_placement_rate
  ) %>%
  arrange(max_increase) %>%
  slice(1) %>%
  ggplot(aes(x = "", y = max_increase, fill = major1)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = scales::percent(max_increase)),
            position = position_stack(vjust = 0.5)) +
  labs(
       x = NULL,
       y = "Percentage Decrease",
       color="Major") +
  theme_minimal() +
  theme(legend.position = "top", legend.box = "horizontal", legend.margin = margin(0, 0, 0, 0))

p_plotly <- ggplotly(p)
p_plotly <- p_plotly %>%
  layout(legend = list(title = list(text = "Major")))
p_plotly
```
