---
title: "Cleaning the Combined BI And Survey Career Data"
author: "Nathan Craft and Elle Prusko"
output:
  html_document:
    date: "`r format(Sys.time(), '%d %B, %Y')`"
    code_folding: hide
    df_print: paged
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float: yes
    code_download: true
  word_document:
    toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
rm(list = ls()) # clear global environment
graphics.off() # close all graphics
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(DataExplorer,tidyverse,readxl,zoo,stargazer,kableExtra,skimr,plotly,ggpubr,vtable,tm)
```

# Introduction and Purpose

The goal of this project is for Nathan Craft and Elle Prusko to answer the question: "What are the macro placement and salary trends we are seeing over the past three years?". To do so, we have identified potential pains for our audience. Such pains consist of:

- Lack of information to better guide students down the right career path
- Finding students high-paying jobs that fit their major
- Deeper understanding of salary trends by industry
- Limited staffing to allocate sufficient time to each student’s needs


To eliminate these pains, we intend to pilot an FSB Placement Analysis where we will visualize and understand salary and placement trends. We will also do external research of salary trends in related industries, and deliver a soundbite of key findings and data-driven recommendations.

# Data Sources

Write something here

## Read in the data

```{r}
data=readRDS(file = "FSB_BI_Survey_2019_2021.rds")
```

# Data Preprocessing

We have data from 3 years of graduates, 2019 - 2021, representing their results from surveys on their career placement results once they left college.

# The rest of your document

Add sections and subsections as necessary to guide your analysis

